---
title: "STA 9750"
---
## About Me

Hi! My name is Stephanie Wu, and I am currently pursuing a Master of Science in Artificial Intelligence and Business Analytics at Baruch College, with a concentration in Operations and Decision Analytics.

I have a background in Fashion Business Management and professional experience as a Business Analyst in the fashion technology and retail analytics industry. I am interested in using data and technology to solve business problems and turn insights into practical strategies.

This website will showcase my projects and work for STA 9750.


```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am a Master's student at <b>Baruch College</b>!")
```

```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`